Pillar 2 - Topic Modeling

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
Delete useless library
graphing functions (works with d_text)

library(modelr) #cross_validation
```

@@

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data){

@@

tf_idf_description <- compute_tf_idf(d_description)
tf_idf_overview    <- compute_tf_idf(d_overview)
tf_idf_manual      <- compute_tf_idf(d_manual)

rm(compute_tf_idf)
```

@@

set.seed(123)
tf_idf_description %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_description")

set.seed(123)
tf_idf_overview %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_overview")

set.seed(123)
tf_idf_manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_manual")

@@

tf_idf_description %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_description")

tf_idf_overview %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_overview")

tf_idf_manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_manual")

>>>>

@@

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```
#DELETE LATERRRRRRRRRRRRRRRRRRRRRRRRRRRRRR
Include d_course
```{r d_course}
load("Output/data_general.RDATA")
d_course <- d_course %>% select(`Course ID`, Cluster) %>% distinct

rm(d_AoD, d_assessment, d_ILO)
```
# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

@@

#
##Application
tf_idf <- map(d_text, .f = compute_tf_idf)

#
##Clean workspace
rm(compute_tf_idf)
```

@@

set.seed(123)
tf_idf$overview %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_overview")

set.seed(123)
tf_idf$manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_manual")

@@

tf_idf$overview %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_overview")

tf_idf$manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_manual")
